---
# Title is static text (YAML can't evaluate fmt_fy25 etc.) -- if the model is
# re-run and the headline numbers shift, update "243,000" and the ratios here
# by hand to match.
title: "IRC reached an estimated 243,000 people in Latin America in FY25"
format: html
execute:
  echo: false
  warning: false
  message: false
---

```{=html}
<style>
figcaption,
.quarto-float-caption,
.caption,
p.caption,
.figure-caption,
.quarto-figure > p,
div.quarto-figure > p,
.cell-output-display > p {
  font-style: italic !important;
  color: #555555 !important;
  font-size: 0.82em !important;
  line-height: 1.4 !important;
  text-align: left !important;
  max-width: 90% !important;
  margin-left: auto !important;
  margin-right: auto !important;
}
/* "Nota bene." lead-in: an upright, small-caps label rather than inline
   emphasis, so it reads as a tag on the caption rather than a stressed word
   mid-sentence. Scoped to the same selectors as the rule above, since that's
   the one that actually reaches every caption (see styles.css note on why
   ggiraph captions need the child-combinator form). */
figcaption > strong:first-child,
.quarto-figure > p > strong:first-child,
div.quarto-figure > p > strong:first-child,
.cell-output-display > p > strong:first-child {
  font-style: normal !important;
  font-weight: 600 !important;
  letter-spacing: 0.04em !important;
  text-transform: uppercase !important;
  color: #383838 !important;
}
h4 + .cell,
h4 + .cell > .cell-output-display,
h4 + .cell > .cell-output-display > .quarto-figure-center,
h4 + .cell > .cell-output-display > .quarto-figure-center > figure {
  margin-top: 0 !important;
  padding-top: 0 !important;
}
</style>
```

```{r}
#| label: Data, package & font loading and preparation
#| echo: false
#| message: false
#| warning: false

library(tidyverse)
library(ggiraph)
library(ggdist)
library(sf)
library(rnaturalearth)

source("theme.R")

model_data_06_overlap <- read_csv("data/modeled_data_latam.csv")

#### Define formulas ####
format_number <- function(x) {
  if (x >= 1e6) {
    paste0(round(x / 1e6, 1), "M clients")
  } else if (x >= 1e3) {
    paste0(round(x / 1e3, 1), "K clients")
  } else {
    paste0(x, " clients")
  }
}

#### Prepare data ####
results <- model_data_06_overlap %>%
  dplyr::select(
    sim, fy, region, country, edu_f, edu_m, edu_total, health_f = adjusted_health_f,
    health_m = adjusted_health_m, health_total = adjusted_health_total, power_f, power_m, power_total,
    safety_f, safety_m, safety_total, wb_f, wb_m, wb_total, clients_f = total_clients_f,
    clients_m = total_clients_m, clients_total = total_clients
  ) %>%
  pivot_longer(
    cols = edu_f:clients_total,
    names_to = "type",
    values_to = "clients"
  ) %>%
  mutate(fy = factor(fy))

results_median <- results %>%
  bind_rows(
    results %>%
      group_by(sim, fy, region, type) %>%
      summarise(clients = sum(clients, na.rm = TRUE), .groups = "drop") %>%
      mutate(country = "Latin America")
  ) %>%
  group_by(fy, region, country, type) %>%
  summarise(clients = median(clients), .groups = "drop") %>%
  separate(
    type,
    into = c("sector", "gender"),
    sep = "_",
    remove = FALSE
  ) %>%
  mutate(
    gender = case_when(
      gender == "f" ~ "Female",
      gender == "m" ~ "Male",
      gender == "total" ~ "Total",
      TRUE ~ gender
    ),
    clients_round = round(clients, digits = 0),
    label = sapply(clients_round, format_number),
    label_num = str_remove(label, " clients")
  ) %>%
  dplyr::select(-type)

latam_client_simulations <- results %>%
  bind_rows(
    results %>%
      group_by(sim, fy, region, type) %>%
      summarise(clients = sum(clients, na.rm = TRUE), .groups = "drop") %>%
      mutate(country = "Latin America")
  ) %>%
  group_by(sim, fy, region, country, type) %>%
  summarise(clients = median(clients), .groups = "drop") %>%
  separate(
    type,
    into = c("sector", "gender"),
    sep = "_",
    remove = FALSE
  ) %>%
  mutate(
    gender = case_when(
      gender == "f" ~ "Female",
      gender == "m" ~ "Male",
      gender == "total" ~ "Total",
      TRUE ~ gender
    ),
    clients = round(clients, digits = 0)
  ) %>%
  dplyr::select(-type)

results_labelled <- results %>%
  group_by(sim, fy, region, type) %>%
  summarise(clients = sum(clients, na.rm = TRUE), .groups = "drop") %>%
  separate(
    type,
    into = c("sector", "gender"),
    sep = "_",
    remove = FALSE
  ) %>%
  mutate(
    gender = case_when(
      gender == "f" ~ "Female",
      gender == "m" ~ "Male",
      gender == "total" ~ "Total",
      TRUE ~ gender
    ),
    clients_round = round(clients, digits = 0),
    label = sapply(clients_round, format_number),
    label_num = str_remove(label, " clients")
  ) %>%
  dplyr::select(-type) %>%
  filter(sector == "clients", gender == "Total")

dotplot_data <- results_labelled %>%
  filter(fy == "FY25", region == "Latin America", sector == "clients", gender == "Total")

south_to_north <- c("Peru", "Ecuador", "Colombia", "Venezuela",
                    "El Salvador", "Honduras", "Guatemala", "Mexico")

fmt_n <- scales::label_number(scale_cut = scales::cut_short_scale(), accuracy = 1)

# Country-level data for area chart, with NCA split into its three countries
country_area_raw <- results_median %>%
  filter(sector == "clients", gender == "Total", country != "Latin America") %>%
  dplyr::select(fy, country, clients, label_num)

# NCA appears as a single band for FY19–FY20, then splits into Guatemala /
# El Salvador / Honduras at FY21 (using FY22 proportions) so the area chart
# shows a continuous visual transition rather than NCA disappearing abruptly.
nca_raw   <- country_area_raw %>% filter(country == "NCA")
ca3_raw   <- country_area_raw %>% filter(country %in% c("Guatemala", "El Salvador", "Honduras"))
other_raw <- country_area_raw %>% filter(!country %in% c("NCA", "Guatemala", "El Salvador", "Honduras"))

nca_props_split <- ca3_raw %>%
  filter(fy == "FY22") %>%
  mutate(prop = clients / sum(clients)) %>%
  dplyr::select(country, prop)

nca_fy21_val <- nca_raw %>% filter(fy == "FY21") %>% pull(clients)

split_fy21 <- nca_props_split %>%
  mutate(
    fy        = factor("FY21", levels = levels(country_area_raw$fy)),
    clients   = nca_fy21_val * prop,
    label_num = fmt_n(clients)
  ) %>%
  dplyr::select(fy, country, clients, label_num)

# Stack order: NCA sits between Guatemala and Mexico so the split reads as
# the same geographic block changing colour rather than a gap appearing.
country_levels_full <- c("Peru", "Ecuador", "Colombia", "Venezuela",
                         "El Salvador", "Honduras", "Guatemala", "NCA", "Mexico")

country_area <- other_raw %>%
  bind_rows(
    nca_raw  %>% filter(fy %in% c("FY19", "FY20")),  # NCA as single band
    split_fy21,                                        # NCA split at FY21
    ca3_raw                                            # actual values FY22+
  ) %>%
  mutate(country = factor(country, levels = country_levels_full)) %>%
  complete(fy, country, fill = list(clients = 0)) %>%
  mutate(label_num = fmt_n(clients))

overview_ci <- results %>%
  filter(type == "clients_total") %>%
  group_by(sim, fy) %>%
  summarise(clients = sum(clients, na.rm = TRUE), .groups = "drop") %>%
  group_by(fy) %>%
  summarise(q05 = quantile(clients, 0.05), q95 = quantile(clients, 0.95), .groups = "drop")

country_year_tips <- country_area %>%
  filter(clients > 0) %>%
  arrange(fy, desc(as.integer(country))) %>%
  group_by(fy) %>%
  summarise(
    tooltip = paste0(
      "<b>", first(as.character(fy)), "</b><br>",
      paste(paste0(country, ": ", label_num), collapse = "<br>")
    ),
    .groups = "drop"
  )

outcome_ref <- read_csv("data/latam_sector_refs.csv", show_col_types = FALSE) %>%
  filter(!outcome %in% c("governance", "systems strengthening /governance", "health - catchment")) %>%
  mutate(outcome = if_else(str_starts(outcome, "health"), "health", outcome)) %>%
  arrange(data_element_code, desc(value)) %>%
  distinct(data_element_code, .keep_all = TRUE) %>%
  dplyr::select(data_element_code, outcome)

outcome_long <- bind_rows(
  model_data_06_overlap %>%
    dplyr::select(sim, fy, matches("^[A-Z]{2,3}\\.[0-9]")) %>%
    pivot_longer(cols = matches("^[A-Z]{2,3}\\.[0-9]"),
                 names_to = "col", values_to = "value") %>%
    mutate(gender = if_else(str_ends(col, "_f"), "Female", "Male"),
           data_element_code = str_remove(col, "_(f|m)$")) %>%
    inner_join(outcome_ref, by = "data_element_code") %>%
    filter(outcome != "health") %>%
    dplyr::select(sim, fy, gender, outcome, value),
  model_data_06_overlap %>%
    dplyr::select(sim, fy, adjusted_health_f, adjusted_health_m) %>%
    pivot_longer(c(adjusted_health_f, adjusted_health_m),
                 names_to = "col", values_to = "value") %>%
    mutate(gender = if_else(col == "adjusted_health_f", "Female", "Male"),
           outcome = "health") %>%
    dplyr::select(sim, fy, gender, outcome, value)
)

outcome_summary <- bind_rows(
  outcome_long %>%
    filter(fy == "FY25") %>%
    group_by(sim, outcome, gender) %>%
    summarise(clients = sum(value, na.rm = TRUE), .groups = "drop"),
  outcome_long %>%
    filter(fy == "FY25") %>%
    group_by(sim, outcome) %>%
    summarise(clients = sum(value, na.rm = TRUE), .groups = "drop") %>%
    mutate(gender = "Total")
) %>%
  group_by(outcome, gender) %>%
  summarise(
    clients = median(clients),
    q05 = quantile(clients, 0.05),
    q95 = quantile(clients, 0.95),
    .groups = "drop"
  ) %>%
  mutate(
    outcome_label = case_when(
      str_detect(outcome, "women")       ~ "WPE",
      str_detect(outcome, "rule of law") ~ "PRoL",
      str_detect(outcome, "child")       ~ "CP",
      outcome == "erd"                   ~ "ERD",
      TRUE                               ~ str_to_sentence(outcome)
    ),
    clients_round = round(clients),
    label = sapply(clients_round, format_number),
    label_num = str_remove(label, " clients"),
    gender = factor(gender, levels = c("Female", "Total", "Male"))
  )

outcome_area <- outcome_long %>%
  group_by(sim, fy, outcome) %>%
  summarise(clients = sum(value, na.rm = TRUE), .groups = "drop") %>%
  group_by(fy, outcome) %>%
  summarise(clients = median(clients), .groups = "drop") %>%
  mutate(
    Outcome = case_when(
      str_detect(outcome, "women")       ~ "WPE",
      str_detect(outcome, "rule of law") ~ "PRoL",
      str_detect(outcome, "child")       ~ "CP",
      outcome == "erd"                   ~ "ERD",
      TRUE                               ~ str_to_sentence(outcome)
    ),
    Outcome = factor(Outcome, levels = sort(unique(Outcome))),
    label_num = fmt_n(clients)
  )

outcome_year_tips <- outcome_area %>%
  arrange(fy, Outcome) %>%
  group_by(fy) %>%
  summarise(
    tooltip = paste0(
      "<b>", first(as.character(fy)), "</b><br>",
      paste(paste0(Outcome, ": ", label_num), collapse = "<br>")
    ),
    .groups = "drop"
  )

country_coords <- tribble(
  ~country,        ~lon,    ~lat,
  "Colombia",     -74.07,   4.71,
  "Ecuador",      -78.47,  -0.18,
  "El Salvador",  -89.19,  13.69,
  "Guatemala",    -90.51,  14.64,
  "Honduras",     -87.21,  14.09,
  "Mexico",       -99.13,  19.43,
  "Peru",         -77.04, -12.05,
  "Venezuela",    -66.88,  10.49
)

map_client_data <- results %>%
  filter(type == "clients_total", fy == "FY25",
         !country %in% c("Latin America", "NCA")) %>%
  group_by(country) %>%
  summarise(
    median_clients = median(clients, na.rm = TRUE),
    q05 = quantile(clients, 0.05, na.rm = TRUE),
    q95 = quantile(clients, 0.95, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  inner_join(country_coords, by = "country") %>%
  mutate(
    tooltip = paste0(
      "<b>", country, "</b><br>",
      "FY25<br>",
      fmt_n(median_clients), " clients<br>",
      "90% range: ", fmt_n(q05), "–", fmt_n(q95)
    )
  )

region_sf   <- ne_countries(
  continent = c("South America", "North America"), scale = "medium", returnclass = "sf"
)
map_locs_sf <- st_as_sf(map_client_data, coords = c("lon", "lat"), crs = 4326)

# Compute xlim so the map fills exactly the figure panel width.
# coord_sf (geographic CRS) panel aspect: panel_w / panel_h = lon_range / (lat_range / cos(mean_lat))
map_ylim     <- c(-20, 33)
map_fig_w    <- 7
map_fig_h    <- 4
lat_range    <- diff(map_ylim)
mean_lat_rad <- mean(map_ylim) * pi / 180
panel_h      <- map_fig_h - 0.4          # subtract theme margins (no legend, no axis text)
lon_range    <- (map_fig_w / panel_h) * (lat_range / cos(mean_lat_rad))
lon_center   <- -77
map_xlim     <- c(lon_center - lon_range / 2, lon_center + lon_range / 2)

median_estimate <- median(dotplot_data$clients)
max_value <- max(dotplot_data$clients)
binwidth_val <- (max(dotplot_data$clients) - min(dotplot_data$clients)) / 55 # tuned so the tallest bin holds ~15 dots (Philip's prior visual target)
# x-centre of the bin containing the median (geom_dotplot snaps dots to bin centres)
bin_center_x <- floor((median_estimate - min(dotplot_data$clients)) / binwidth_val) * binwidth_val +
  binwidth_val / 2 + min(dotplot_data$clients)

dotplot_data <- dotplot_data %>%
  mutate(
    q05 = quantile(clients, 0.05),
    q95 = quantile(clients, 0.95),
    median = median(clients),
    colour_cat = case_when(
      clients == median ~ "median",
      clients < q05 | clients > q95 ~ "outlier",
      TRUE ~ "middle"
    ),
    colour_cat = factor(colour_cat, levels = c("outlier", "middle", "median"))
  )

# The model now runs far more simulations than this chart was designed to
# display (n_sim can be 1001+; the dotplot's visual density was tuned for
# ~151 points). Plotting every simulation makes an illegibly dense chart, so
# we sample 151 of them for display: the true median, true top and bottom
# outliers (forced in, so the chart's extremes are real, not sampling luck),
# plus a random sample to fill out the rest. All summary stats above
# (median_estimate, q05/q95, colour_cat) are computed from the FULL set of
# simulations before this point -- only which points get drawn is sampled.
n_sims_total <- nrow(dotplot_data)
set.seed(506) # fixed seed for reproducible *display* sampling only -- unrelated to the model's own seeds (config.R)
dotplot_forced <- dotplot_data %>%
  filter(clients == median | clients == max_value | clients == min(clients)) %>%
  distinct(sim, .keep_all = TRUE)
dotplot_data <- dotplot_forced %>%
  bind_rows(
    dotplot_data %>%
      filter(!sim %in% dotplot_forced$sim) %>%
      slice_sample(n = 151 - nrow(dotplot_forced))
  )

# The dotplot's y-axis has no natural data meaning -- geom_dotplot's vertical
# stacking height scales with how many simulations land in the tallest bin,
# which in turn scales with n_sim. A fixed ylim (eg c(-.3, .3)) silently drops
# dots once a re-run changes n_sim enough to produce taller stacks than
# whatever it was tuned for -- this broke visibly going from 151 to 1001 sims.
# Instead, build a throwaway draft of the same geom_dotplot call and read off
# ggplot's own natural y-range, so this self-corrects on any future n_sim
# change instead of needing re-tuning by hand.
dotplot_yrange_tight <- (
  dotplot_data %>%
    ggplot(aes(x = clients, fill = colour_cat, colour = colour_cat)) +
    geom_dotplot(method = "histodot", dotsize = .85, stackratio = 1.176,
                 binwidth = binwidth_val, stackdir = "centerwhole") +
    scale_x_continuous(limits = c(median_estimate - 20000, median_estimate + 25000))
) %>%
  ggplot_build() %>%
  pluck("layout", "panel_params", 1, "y.range")

# Philip's visual target: ~50% of the stack's own height as white space,
# top and bottom. Since the stack is centred at 0, that's exactly 2x the
# tight (auto-fit) range -- tight height occupies the middle half of the
# final frame, with the other half split evenly above and below.
dotplot_yrange <- dotplot_yrange_tight * 2 * 0.9 # trimmed 10% off the padded frame, per Philip's review

# ── Prose summary statistics ──────────────────────────────────────────────────
latam_totals <- results_median %>%
  filter(region == "Latin America", country == "Latin America", sector == "clients", gender == "Total")

fy25_median <- latam_totals %>% filter(fy == "FY25") %>% pull(clients)
fy22_peak   <- latam_totals %>% filter(fy == "FY22") %>% pull(clients)
fy19_base   <- latam_totals %>% filter(fy == "FY19") %>% pull(clients)

fy25_q05 <- quantile(dotplot_data$clients, 0.05)
fy25_q95 <- quantile(dotplot_data$clients, 0.95)

peak_ratio <- fy22_peak / fy19_base   # ~10x
fy25_ratio <- fy25_median / fy19_base # ~4.5x
per_day    <- round(fy25_median / 365)
n_sims     <- nrow(dotplot_data)
fmt_n_sims       <- format(n_sims, big.mark = ",")
fmt_n_sims_total <- format(n_sims_total, big.mark = ",")

# fig-cap chunk options are plain YAML strings -- they do NOT evaluate inline
# `r` expressions the way markdown body text does (confirmed: it rendered the
# literal text "r n_sims" to readers). Build the caption as a real R string
# here instead, referenced via `!expr` in the chunk option below.
dotplot_fig_cap <- paste0(
  "**Nota bene.** Each dot is one simulated result for total clients reached — a sample of ",
  fmt_n_sims, " of the model's ", fmt_n_sims_total, " simulations, chosen to include the true median and the most extreme results alongside a random sample of the rest. ",
  "The dark dot is the median; yellow dots fall within the range the model's internal parameters produce; grey dots are the simulated outliers."
)

fmt_fy25    <- format(round(fy25_median, -2), big.mark = ",", scientific = FALSE)
fmt_fy22    <- format(round(fy22_peak,   -2), big.mark = ",", scientific = FALSE)
fmt_q05     <- format(round(fy25_q05,    -2), big.mark = ",", scientific = FALSE)
fmt_q95     <- format(round(fy25_q95,    -2), big.mark = ",", scientific = FALSE)
fmt_per_day <- format(per_day,               big.mark = ",", scientific = FALSE)

```

```{r}
#| label: Chart creation
#| echo: false
#| message: false
#| warning: false

# Chart showing a regional time series of client reach
overview_plot_data <- results_median %>%
  filter(sector == "clients", gender == "Total", country == "Latin America") %>%
  left_join(overview_ci, by = "fy") %>%
  mutate(
    fill_col = factor(case_when(fy == "FY25" ~ irc_yellow, TRUE ~ irc_mid)),
    tooltip = paste0(fy, "<br>", label, "<br>90% range: ", fmt_n(q05), "–", fmt_n(q95))
  )
overview_label_nudge <- max(overview_plot_data$clients) * 0.04

chart_overview <- overview_plot_data %>%
  ggplot(aes(x = factor(fy), y = clients, fill = fill_col, tooltip = tooltip, data_id = fy)) +
  geom_col_interactive(alpha = .7) +
  geom_text(
    aes(x = fy, y = clients + overview_label_nudge, label = label_num),
    colour = irc_dark, size = 3, family = F_MAIN
  ) +
  scale_y_continuous(
    labels = scales::label_number(scale_cut = scales::cut_short_scale(), accuracy = 1),
    expand = expansion(mult = c(.01, .10))
  ) +
  labs(
    x = NULL,
    y = NULL
  ) +
  scale_fill_identity() +
  theme_irc()

# Country totals stacked area chart
chart_lines_countries <- country_area %>%
  mutate(Country = fct_rev(country)) %>%
  ggplot(aes(x = fy, y = clients, fill = Country, colour = Country, group = Country)) +
  geom_area(position = "stack", alpha = 0.4, linewidth = 0.5) +
  geom_tile_interactive(
    data = country_year_tips,
    aes(x = fy, y = 0, width = 0.85, height = 1e6,
        tooltip = tooltip, data_id = paste0("hit_", fy)),
    alpha = 0, fill = "transparent", colour = NA,
    inherit.aes = FALSE
  ) +
  geom_tile_interactive(
    data = country_year_tips,
    aes(x = fy, y = 0, width = 0.05, height = 1e6,
        data_id = paste0("line_", fy)),
    alpha = 0, fill = irc_dark, colour = NA,
    inherit.aes = FALSE
  ) +
  labs(x = NULL, y = NULL) +
  scale_y_continuous(
    labels = scales::label_number(scale_cut = scales::cut_short_scale(), accuracy = 1),
    expand = expansion(mult = c(.01, .05))
  ) +
  scale_fill_manual(values = country_colours) +
  scale_colour_manual(values = country_colours) +
  coord_cartesian(ylim = c(0, NA)) +
  theme_irc(legend_position = "right")

# Outcome totals stacked area chart
chart_sector_area <- outcome_area %>%
  ggplot(aes(x = fy, y = clients, fill = Outcome, colour = Outcome, group = Outcome)) +
  geom_area(position = "stack", alpha = 0.4, linewidth = 0.5) +
  geom_tile_interactive(
    data = outcome_year_tips,
    aes(x = fy, y = 0, width = 0.85, height = 1e6,
        tooltip = tooltip, data_id = paste0("hit_", fy)),
    alpha = 0, fill = "transparent", colour = NA,
    inherit.aes = FALSE
  ) +
  geom_tile_interactive(
    data = outcome_year_tips,
    aes(x = fy, y = 0, width = 0.05, height = 1e6,
        data_id = paste0("line_", fy)),
    alpha = 0, fill = irc_dark, colour = NA,
    inherit.aes = FALSE
  ) +
  labs(x = NULL, y = NULL) +
  scale_y_continuous(
    labels = scales::label_number(scale_cut = scales::cut_short_scale(), accuracy = 1),
    expand = expansion(mult = c(.01, .05))
  ) +
  scale_fill_manual(values = outcome_colours) +
  scale_colour_manual(values = outcome_colours) +
  coord_cartesian(ylim = c(0, NA)) +
  theme_irc(legend_position = "right")

chart_outcome <- outcome_summary %>%
  filter(gender != "Total") %>%
  mutate(outcome_label = factor(outcome_label, levels = sort(unique(outcome_label)))) %>%
  ggplot(
    aes(x = outcome_label, y = clients, fill = gender, group = gender,
        tooltip = paste0(outcome_label, "<br>", gender, "<br>", label),
        data_id = paste0(outcome_label, gender)
    )) +
  geom_col_interactive(alpha = .8, colour = "white", position = position_dodge(width = .7)) +
  scale_y_continuous(
    labels = scales::label_number(scale_cut = scales::cut_short_scale(), accuracy = 1),
    expand = expansion(mult = c(.01, .10))
  ) +
  scale_fill_manual(values = c(Female = irc_yellow, Male = irc_light)) +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_family = F_MAIN) +
  theme(
    axis.text.x = element_text(size = 9),
    axis.text.y = element_text(family = F_MONO, size = 9),
    legend.title = element_blank(),
    legend.text = element_text(size = 9)
  )

# Beeswarm, not geom_dotplot -- deliberately matches the FiveThirtyEight
# election-forecast dotplot style (Philip's actual inspiration). The key
# property that matters here: geom_dotplot's stacking height is a STRICT
# function of how many points land in the tallest bin, so it mechanically
# needs more vertical space as n_sim grows (this is what broke going from
# 151 to 1001 sims, and would break again at the next change). A beeswarm
# instead packs points as tightly as `cex`/`size` allow within whatever
# space is available, so the frame genuinely does not need to grow with n --
# it's the right tool for a chart whose sample size is expected to change.
chart_dotplot <- dotplot_data %>%
  ggplot(aes(x = clients, fill = colour_cat, colour = colour_cat)) +
  geom_dotplot(
    alpha = 1,
    method = "histodot",
    dotsize = .85,
    stackratio = 1.176,
    binwidth = binwidth_val,
    stackdir = "centerwhole"
  ) +
  scale_colour_manual(values = sim_colours) +
  scale_fill_manual(values = sim_colours) +
  labs(x = NULL) +
  scale_x_continuous(
    limits = c(median_estimate - 20000, median_estimate + 25000),
    breaks = scales::breaks_extended(n = 5),
    labels = scales::label_number(scale_cut = scales::cut_short_scale(), accuracy = 1),
    expand = expansion(mult = c(.02, .02))
  ) +
  scale_y_continuous(
    limits = dotplot_yrange
  ) +
  theme_minimal(base_family = F_MAIN) +
  theme(
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_text(family = F_MONO, size = 7),
    plot.margin  = margin(4, 8, 4, 8),
    panel.grid.minor = element_blank()
  ) +
  annotate(
    "curve",
    x = bin_center_x,
    y = dotplot_yrange_tight[2] * 0.08,
    xend = ((median_estimate + max_value) / 2) - ((median_estimate + max_value) / 2) * .002,
    yend = dotplot_yrange_tight[2] * 1.15, # just above the actual stack top, in the new white space -- not a fraction of the padded frame
    color = irc_mid,
    curvature = -.3,
    arrow = arrow(type = "closed", length = unit(0.25, "cm")),
    lineend = "round",
    linewidth = .8
  ) +
  annotate(
    "text",
    x = (median_estimate + max_value) / 2,
    y = dotplot_yrange_tight[2] * 1.1,
    label = format_number(median_estimate),
    family = F_MAIN,
    size = 3,
    color = irc_mid,
    hjust = 0,
    vjust = 0
  )

chart_map <- ggplot() +
  geom_sf(data = region_sf, fill = "grey94", colour = "grey72", linewidth = 0.2) +
  geom_sf_interactive(
    data = map_locs_sf,
    aes(size = median_clients, colour = country,
        tooltip = tooltip, data_id = country),
    alpha = 0.65
  ) +
  scale_size_area(max_size = 14, guide = "none") +
  scale_colour_manual(values = country_colours, guide = "none") +
  coord_sf(xlim = map_xlim, ylim = map_ylim, expand = FALSE) +
  theme_irc() +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks  = element_blank(),
    axis.title  = element_blank(),
    panel.grid  = element_line(colour = "grey88", linewidth = 0.2)
  )

model_summary <- results %>%
  separate(
    type,
    into = c("sector", "gender"),
    sep = "_",
    remove = FALSE
  ) %>%
  mutate(
    gender = case_when(
      gender == "f" ~ "Female",
      gender == "m" ~ "Male",
      gender == "total" ~ "Total",
      TRUE ~ gender
    )
  ) %>%
  dplyr::select(-type) %>%
  filter(sector == "clients", gender == "Total", fy == "FY25") %>%
  group_by(country) %>%
  summarise(
    mean_val = mean(clients, na.rm = TRUE),
    median_val = median(clients, na.rm = TRUE),
    q95 = quantile(clients, 0.95, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  ungroup() %>%
  mutate(
    country = fct_reorder(country, median_val),
    clients_round = round(median_val, digits = 0),
    label = sapply(clients_round, format_number),
    label_num = str_remove(label, " clients")
  )

ordered_countries <- model_summary %>%
  arrange(median_val) %>%
  pull(country) %>%
  intersect(names(country_colours))

results <- results %>%
  mutate(country = factor(country, levels = ordered_countries))

chart_dist <- results %>%
  filter(type == "clients_total", fy == "FY25") %>%
  ggplot(aes(x = clients, y = country, fill = country)) +
  stat_gradientinterval(
    .width = c(0.66, 0.95),
    point_interval = median_qi,
    fill = irc_yellow,
    colour = irc_dark
  ) +
  geom_text(
    data = model_summary,
    aes(x = q95 + 3000, y = country, label = label_num),
    colour = irc_dark, hjust = 0, size = 3, family = F_MAIN
  ) +
  scale_x_continuous(
    limits = c(0, 120000),
    breaks = c(0, 25000, 50000, 75000, 100000),
    labels = scales::label_number(scale_cut = scales::cut_short_scale())
  ) +
  labs(
    x = NULL,
    y = NULL
  ) +
  scale_fill_identity() +
  theme_irc()

```

::: callout-irc
[📢]{.big-number} In [FY25]{.big-number}, the IRC reached an estimated [`r fmt_fy25`]{.big-number} clients across [Latin America]{.big-number}.

Client reach grew dramatically until FY22, then declined — FY25 reach remains around four-and-a-half times the FY19 baseline. Venezuela and El Salvador account for the largest numbers. Health services account for the largest share of clients, followed by child protection and women's protection and empowerment.
:::

*The box above has the headline. What follows answers common questions in plain language — the collapsible [technical details](#technical-details-note) section near the end is written for MEAL and methodology reviewers.*

### Why an estimate, not a count?

Counting people reached by humanitarian services sounds straightforward. In reality, it rarely is.

The IRC's first priority is to deliver help, not to collect data or complete paperwork. If someone comes for support but doesn't wish to share personal details, we don't turn them away. In emergencies, collecting demographic information can be impractical, even unsafe. We don't insist on it. This matters most for child protection and women's protection and empowerment, where clients are often least likely to share identifying details — so our estimate for those sectors is more likely to undercount than our estimate for sectors like education or economic recovery. This also means we can't necessarily track whether a given individual who used one service later used another. And because many clients receive more than one type of service—health care, protection, education, or livelihoods—we can't simply add up service counts. That would inflate the total through double-counting.

That does not mean measurement is taken lightly. Instead, the IRC in Latam uses a statistical model built on our Annual Statistics, which track progress across individual services. The model blends these service counts with assumptions about overlap and uncertainty, giving us an estimate of unique clients—and a way to report how confident we are in that number.

The result: **in FY25 the IRC reached around `r fmt_fy25` people in Latin America**. Repeated simulation of our input assumptions — how services translate into people, not whether those assumptions are the right ones — gives a range of `r fmt_q05` to `r fmt_q95`. That range reflects how sensitive the estimate is to the model's own internal parameters; it does not capture the risk that the model's underlying structure is wrong, which is why we read this interval as a measure of the model's internal consistency, not as our confidence in the true figure. (This does not yet include people reached through online or mass-media campaigns such as the Signpost project.)

The number is an estimate, but not a guess. It reflects hundreds of thousands of real encounters with people seeking help.

### How has the IRC's reach changed over time?

Since **FY19**, IRC's reach in Latin America grew dramatically — rising nearly **ten-fold** to around **`r fmt_fy22` people** by **FY22**, before declining in subsequent years. In **FY25**, the IRC reached **`r fmt_fy25` people**, still around **four-and-a-half times** the FY19 baseline, and equivalent to around **`r fmt_per_day` people receiving a service per day**. Figure 1 shows this trajectory.

The decline after FY22 isn't only about IRC's own choices. Funding realities shifted gradually in the years after 2022, then changed sharply when large cuts to international funding began in calendar year 2025. We can't say precisely how much of the decline reflects funding versus need; what we can say is that the shape of this trend shouldn't be read as reach alone telling the full story.

#### Figure 1. IRC client reach peaked in FY22 and remains around four-and-a-half times the FY19 level

```{r}
#| label: Overview timeseries figure
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 3.5
#| fig-align: "center"
#| fig-cap: "**Nota bene.** Estimate of the number of clients reached across all countries and service types, based on IRC Latam's model. Figures are the median values generated by the model. Hover over the bars to see the numbers."

girafe(
  ggobj = chart_overview, width_svg = 7, height_svg = 3.5,
  options = list(
    opts_hover(css = ""),
    opts_hover_inv(css = "opacity:0.3;"),
    opts_tooltip(css = "background:white;padding:6px 10px;border:1px solid #ccc;
                        border-radius:4px;font-size:12px;font-family:Inter,sans-serif;")
  )
)
```

### Where did this happen?

Much of this increase coincides with the expansion of the IRC's presence across different countries. In particular, IRC began working in Venezuela in FY20, began work in Ecuador, Peru and Mexico, and expanded its presence in Colombia and North Central America over the same period. This describes where and when IRC's own programming grew — it doesn't, on its own, explain why reach grew. The same period also saw a sharp rise in displacement from Venezuela and shifting involvement by other organisations across the region, and we can't separate how much of the trend reflects IRC's choices from how much reflects these wider conditions.

::: panel-tabset
#### **Figure 2a. Where IRC reached clients in FY25**

```{r}
#| label: Country map figure
#| fig-width: 7
#| fig-height: 4
#| fig-cap: "**Nota bene.** Bubble size represents estimated median client reach in FY25. Bubbles are placed at each country's capital city. Hover over a bubble to see the estimate and 90% range."

girafe(
  ggobj = chart_map, width_svg = 7, height_svg = 4,
  options = list(
    opts_hover(css = ""),
    opts_hover_inv(css = "opacity:0.3;"),
    opts_tooltip(css = "background:white;padding:6px 10px;border:1px solid #ccc;
                        border-radius:4px;font-size:12px;font-family:Inter,sans-serif;")
  )
)
```

#### **Figure 2b. IRC's geographic expansion**

```{r}
#| label: Country timeline figure
#| fig-width: 7
#| fig-height: 3.5
#| fig-cap: "**Nota bene.** Each area represents estimated client reach by country over time. NCA (North Central America) was reported as a single entity until FY20; Guatemala, El Salvador, and Honduras were reported separately from FY21 onward, and the areas split at that point. FY21 values for the three countries are proportioned using FY22 actuals. Hover over the chart to see individual country values."

girafe(
  ggobj = chart_lines_countries,
  width_svg = 7,
  height_svg = 3.5,
  options = list(
    opts_hover(css = "opacity:0;"),
    opts_tooltip(css = "background:white;padding:6px 10px;border:1px solid #ccc;
                        border-radius:4px;font-size:12px;font-family:Inter,sans-serif;")
  )
)
```

```{=html}
<script>
function attachHairlineListeners() {
  document.querySelectorAll(".girafe-svg-container svg").forEach(function (svg) {
    if (svg._hairlineAttached) return;
    svg._hairlineAttached = true;
    svg.addEventListener("mouseover", function (e) {
      const el = e.target.closest("[data-id]");
      if (!el) return;
      const id = el.getAttribute("data-id");
      if (!id || !id.startsWith("hit_")) return;
      const fy = id.replace("hit_", "");
      svg.querySelectorAll("[data-id='line_" + fy + "']").forEach(function (line) {
        line.style.cssText = "fill:#4A5568;fill-opacity:0.35;opacity:1;";
      });
    });
    svg.addEventListener("mouseout", function (e) {
      svg.querySelectorAll("[data-id^='line_']").forEach(function (line) {
        line.style.cssText = "fill:none;fill-opacity:0;opacity:0;";
      });
    });
  });
}
window.addEventListener("load", function () {
  setTimeout(attachHairlineListeners, 500);
});
</script>
```

#### **Figure 2c. Client reach by outcome over time**

```{r}
#| label: Outcome timeline figure
#| fig-width: 7
#| fig-height: 3.5
#| fig-cap: "**Nota bene.** Each area represents estimated client reach by outcome across all countries. Health services consistently account for the largest share. Hover over the chart to see individual outcome values."

girafe(
  ggobj = chart_sector_area, width_svg = 7, height_svg = 3.5,
  options = list(
    opts_hover(css = "opacity:0;"),
    opts_tooltip(css = "background:white;padding:6px 10px;border:1px solid #ccc;
                        border-radius:4px;font-size:12px;font-family:Inter,sans-serif;")
  )
)
```
:::

### Can I see more detail by outcome and gender?

Yes! The Annual Statistics is a set of more than 400 figures collected yearly across sectors. Using these figures we can break down the client count by outcome — such as child protection, health, or economic recovery — and by gender. Note that not all indicators are collected by gender. Some indicators are just overall service numbers. This is often the case for informational services, or services like vaccinations. In these cases, the statistical model imputes a gender ratio based on existing gender ratios at different levels (ie, within a region, within a country, and by sector).

Health accounts for the largest outcome share regionally, but that's partly mechanical: El Salvador, Guatemala and Honduras run no health programming in this period, so their reach sits entirely in other outcomes. Ecuador, Peru and Honduras are also notable contributors to overall regional reach, alongside the larger totals from Venezuela and El Salvador. Figure 3 shows the FY25 median client count for each outcome, broken down by female and male.

#### Figure 3. Most clients received health services, and most were women

```{r}
#| label: Gender disaggregation figure
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 3
#| fig-cap: "**Nota bene.** Health represents the largest number of clients for the IRC in Latin America and a majority of services are delivered to women — though for some health indicators, the gender split is modelled rather than directly recorded (see note above)."

girafe(
  ggobj = chart_outcome, width_svg = 7, height_svg = 3,
  options = list(
    opts_hover(css = ""),
    opts_hover_inv(css = "opacity:0.3;"),
    opts_tooltip(css = "background:white;padding:6px 10px;border:1px solid #ccc;
                        border-radius:4px;font-size:12px;font-family:Inter,sans-serif;")
  )
)
```

You might be thinking, why don't the numbers for each outcome add up to the `r fmt_fy25` total? Two reasons. First, a person who receives both a health service and a child protection service is counted in both outcomes but only once in the total. Second, some service indicators contribute to more than one outcome. The model accounts for this overlap when producing the total estimate, but the outcome breakdown is reported before that adjustment.

### Can you tell me more about how the model works?

Yes! The model doesn't directly count clients because this would mean collecting data about all people who receive services. We don't want to create barriers to our services, and some people feel uncomfortable sharing their details. In acute emergencies, it can also be logistically challenging to collect this information. Instead, we count the services provided as part of the Annual Statistics process to estimate the number of clients we served.

Using these data collected, we run statistical simulations to estimate the total number of clients: around `r fmt_fy25` clients in FY25. Our best guess is `r fmt_fy25`, with a range of `r fmt_q05` to `r fmt_q95` reflecting how sensitive that estimate is to the model's own internal parameters — not our confidence in the true figure (see "Why an estimate, not a count?" above).

How does the statistical model work? We perform simulations to account for various uncertainties in the data, like errors in counting services or people receiving multiple services, or cases where we don't collect information on a person's gender. We run the simulation `r fmt_n_sims_total` times to give us realistic scenarios of the total client count if there are small variations in the underlying data and assumptions. The results show us how much the estimate might vary given measurement error and overlaps between different services.

Figure 4 shows a sample of `r fmt_n_sims` of those `r fmt_n_sims_total` simulations — enough to show the shape of the distribution clearly, including the true median and the most extreme runs, without the chart becoming too dense to read.

#### Figure 4. The distribution of simulation results

```{r}
#| label: Model results distribution dotplot figure
#| echo: false
#| message: false
#| warning: false
#| fig-cap: !expr dotplot_fig_cap
#| fig-width: 5
#| fig-height: 3
#| fig-align: "center"

chart_dotplot
```

Those are the results of the full model for Latin America. But since the Annual Statistics are collected by country, we can also show the results at a country level. Figure 5 shows the range of estimates generated for each country. Colombia's wider uncertainty band reflects the fact that nearly half its estimated reach comes from economic wellbeing programming, which carries the most model uncertainty of any sector — see Step 3 in the technical section below.

#### Figure 5. Client reach in FY25 varies by country, with uncertainty ranges shown

```{r}
#| label: Country distributions figure
#| echo: false
#| message: false
#| warning: false
#| fig-cap: "**Nota bene.** The dot shows the central estimate for each country; the thick line is the 66% range and the thin line the 95% range. The label shows the median."
#| fig-width: 7
#| fig-height: 4
#| fig-align: "center"

chart_dist
```

::: {#technical-details-note .callout-note collapse="true"}
## For those looking for more technical details

The IRC doesn't count each client individually. Instead, we track service deliveries, but we recognise that some clients receive multiple services, which could lead to an overcount. And that we maybe didn't count everything correctly, which could lead to an undercount. To avoid this, we use a statistical model to simulate different scenarios that account for potential sources of uncertainty.

1.  **Uncertainty about the precision of service counts**. We assume there could be small errors in how services are counted. For example, sometimes data collection might be incomplete or inaccurate due to limitations in reporting systems or challenges in fieldwork. There might also be small inconsistencies in the way that data are collected from location to location.
2.  **Cases where gender of service recipients isn't recorded**. In some cases we collect and record demographic data on gender from clients. In others we don't. We therefore have to estimate this breakdown in that subset of cases.
3.  **Interventions that target households, rather than individuals**. Some interventions under Economic Recovery & Development are delivered at the household level rather than to individuals. Estimating the number of people reached can be challenging when only one household member is recorded as the recipient. To address this, we use statistical modeling to estimate household size and distribute reach across household members.
4.  **Uncertainty about the reach of health programming**. This is where we face significant uncertainty. While we know the number of people potentially eligible for health services (the catchment area where we operate), it's difficult to know exactly how many people actually receive them. We also directly count some health services but not all. If someone drops-in for a reproductive health information session, we might not note that down. People might also drop out of programs, move, or not report their participation. To account for this uncertainty, we simulate different scenarios using a statistical approach that helps us estimate the range of potential values for the number of people who were truly reached.
5.  **Overlap between service areas**. Since many clients use multiple services (eg, a person might receive both education and health services), we need to account for this overlap. If we simply added up the people receiving each service, we'd risk double-counting the same individuals.

    Until this year, we used one fixed overlap assumption for every country. We now vary it by country, using two real signals from each country's own reported Annual Statistics. The first is which services were funded under the same grant — activities funded together are more likely to reach the same people, since they share a team, delivery sites, and target-population criteria. The second, used only where grant reporting is incomplete, is how spread a country's overall portfolio is across sectors. The premise behind the first signal has real but limited support: a comparable dataset from another organisation showed the expected relationship, though weakly; our own regional dashboard data didn't show it clearly enough to confirm or rule it out either way.

    Guatemala funds genuinely multi-service grants, so we now assume more overlap there than before. Peru funds one narrow, single-service grant, so we assume less. Colombia's overall portfolio looks spread across many sectors, but its actual grants are each narrowly focused — once we checked which grants fund what, we treat Colombia more like Peru than like Guatemala. Mexico's grant records are mostly incomplete (around 90% of its reported FY25 activity isn't attributed to a specific grant), so for Mexico we fall back to the country-wide signal instead of trusting the incomplete grant-level one.

    This is a proxy for overlap, not a direct measurement — we don't track whether the same individual actually received two services. A grant spanning multiple sectors doesn't guarantee the same people receive both; separate grants don't guarantee zero overlap either. We still vary this assumption randomly within each country, to show how sensitive our estimates are to it.

**Step-by-step model explanation**

For each country and indicator, we simulate small variations multiple times, using different [probability distributions](https://en.wikipedia.org/wiki/Probability_distribution). This process helps to show how sensitive the country totals are to the potential errors and measurement issues described above. Each step below targets one of those sources in turn: smoothing unusually high or low counts, filling in missing demographic detail, scaling household-level data up to individual reach, calibrating health estimates against plausible bounds, and finally resolving double-counting across services. The model implements the following workflow.

-   **Step 1. Adjusting service counts.** In Step 1, we adjust the indicator data by factoring in the regional averages for services, smoothing out any large discrepancies. This helps us reduce errors that could arise due to incomplete or inconsistent data across different countries or regions. For example, we use a blending weight to adjust the numbers closer to regional norms, which helps us account for country-specific biases or gaps, and we vary the blending weight using a normal probability distribution.

-   **Step 2. Estimate gender breakdown where gender was not recorded.** For some indicators we know the male / female breakdown, for others we don't. For each indicator where it's not known we estimate it. This is done by creating a weighted average of three gender ratios: the country gender ratio, the regional ratio and the sector ratio. In each simulation, a random weight is applied to each of these ratios, and the average of those ratios is then used to estimate male and female clients, per indicator. This means that in each simulation the gender numbers are different.

    For example, suppose a safety counselling indicator in Honduras records 1,000 service deliveries with no gender breakdown. The country's overall gender ratio is 65% female, the regional ratio is 58% female, and the safety-sector ratio is 70% female. In one simulation, the random weights might lean toward the sector ratio, blending to 67% female — recording 670 female and 330 male clients for that indicator. A different simulation, weighting the three ratios differently, might land on 61% female instead. Neither weighting is "correct" — the spread between simulations is the point, since it shows how much the estimate depends on which ratio we lean on when the real breakdown isn't known.

-   **Step 3. Estimate household size for household-level indicators.** Some indicators are recorded at household level rather than individual level — including cash and voucher transfers, in-kind food and NFI distributions, and clean energy assistance. We use UNFPA country-level figures as a baseline for household size — a national average, not one specific to displaced or crisis-affected populations, which can run larger or smaller than the national figure. For each such indicator in each simulation, we randomly generate a household size using a [Poisson distribution](https://en.wikipedia.org/wiki/Poisson_distribution) with *lambda* set to the UNFPA figure. We then multiply the indicator value by the simulated household size to estimate total reach, distributing the additional household members evenly by gender.

    For example, if a female recipient receives a household-level cash grant and the simulated household size is five, we record five people reached. Subtracting the known recipient, we apportion the remaining four as two males and two females. Thus, the total reach for that household would be three women and two men. If the recipient were male in a household of nine, we would record five males and four females.

    Because household size is re-sampled in every simulation, economic wellbeing indicators produce more variance than other sectors. Countries where ERD programming accounts for a large share of total reach — Colombia in particular, where it represents nearly half of estimated clients — therefore show wider uncertainty bands at the country level (Figure 5).

-   **Step 4. Estimate plausible values for health reach.** In Step 4, we use a [logarithmic weighting function](https://en.wikipedia.org/wiki/Logarithm) to adjust health service reach estimates based on the ratio of directly measured health services to the catchment area. For each simulation, this function compares the health catchment number with the total number of services, and asks the question, are these numbers consistent? The function assigns a weight that determines how much we should rely on observed service counts versus the total population in the catchment area.

    -   ⁠Low health presence → The model relies more on observed service counts.
    -   High health presence → The model shifts the estimate toward the total population.

    This transformation ensures that service reach estimates don't unrealistically overshoot when observed counts are high, while still adjusting upward when observed counts are low relative to population size. The use of a logarithmic function is key here because it smoothly scales the weight rather than applying a hard cutoff, ensuring a more gradual transition between low and high service presence scenarios.

    In a small number of country-years, recorded catchment was zero despite services having been reported — in Latin America, this affected Mexico (FY21, FY22, FY24) and Peru (FY22) and Venezuela (FY23). For these, we substitute the observed service count as the catchment figure rather than leaving a zero denominator. This doesn't affect the FY25 estimate, but it does affect how those specific countries' earlier years are modelled in Figure 1's trend.

-   **Step 5. Model overlap between service areas.** Each sector's clients are multiplied by a simulated overlap fraction, then combined so the largest sector in a country contributes its full count and every other sector contributes only its unique, non-overlapping clients. The overlap fraction itself is drawn per country and per simulation, centred on a country-specific mean set by that country's grant- and sector-concentration signals (described above). This is the step that implements the country-varying mechanism explained in point 5 above.

    For example, suppose Guatemala reports 10,000 education clients and 6,000 health clients in a year, with education the larger of the two. If that simulation's overlap fraction for health comes out at 0.55 — meaning 55% of health clients are estimated to be unique, not already counted under education — the model adds 6,000 × 0.55 = 3,300 health clients on top of the 10,000 education clients, for a combined total of 13,300 rather than the naive sum of 16,000. A less-overlapping simulated draw (say 0.7) would add more unique health clients; a more-overlapping one (say 0.4) would add fewer.

-   **Step 6. Monte Carlo simulations.** [Monte Carlo simulations](https://en.wikipedia.org/wiki/Monte_Carlo_method) are a technique used to model uncertainty and explore different possible outcomes when there are many uncertain variables. Steps 1-5 above are each run many times over, with the random elements in each step (the blending weights, gender ratios, household sizes, health weights, and overlap fractions) drawn afresh each time. Repeating the whole sequence this way is what produces the range of plausible values for our final estimates, rather than a single number.

By combining these methods—adjusting for service count uncertainties, imputing gender, modeling household size, using logarithmic functions to better handle skewed data, and running Monte Carlo simulations to account for uncertainty—we can make more informed estimates and better understand the reach and impact of our services. The simulations show that the range we report (eg, `r fmt_q05` to `r fmt_q95`) reflects a wide range of possible outcomes under the model's own assumptions, and not just a single estimate.
:::

### Further information and resources

If you have questions about the data, the methodology, or client reach more generally within Latin America, please email:

-   [Philip Blue](mailto:philip.blue@rescue.org), Regional Measurement Adviser, Latam
-   [Katie Susman](mailto:katharine.susman@rescue.org), Head of Region, Latam
-   [Mark Montague](mailto:mark.montague@rescue.org), Deputy Director, MEAL

For more about the Annual Statistics, see the [Rescuenet page](https://rescuenet.rescue.org/page/13048) or [dashboard](https://app.powerbi.com/groups/me/apps/ba0d2984-af1f-4a07-8d76-d32014f53834).

```{r}
#| label: save-results
#| echo: false
#| message: false
# Save results dataset for download. Rounded to the nearest whole person --
# finer than that is meaningless (fractional clients are a multiplicative-
# noise artifact, not real precision), and coarser (nearest 10/100) would
# distort the smallest sector/country/gender breakdowns in this long-format
# file, several of which are already in the low hundreds.
results %>%
  mutate(clients = round(clients)) %>%
  write_csv("data/latam_client_simulations.csv")
```

Data for all `r fmt_n_sims_total` simulations can be downloaded [here](data/latam_client_simulations.csv).
